Supplemental Online Materials

### 2022-09-13 Documents/supplemental-materials.Rmd
preprint

>>>>

# Experiment 3

### Measures

We included additional measures not used in the analyses reported in this paper.

We included a three-item measure of moral conviction [@ryan_reconsidering_2014] that assessed to what extent participants' feelings about restricting or banning abortion were, for example, connected to their core moral beliefs or convictions (1 = *not at all*, 5 = *very much*).

We measured gender-related system-justifying beliefs with eight items [adapted from @jost_exposure_2005], for example, "in general, relations between men and women are fair" (1 = *strongly disagree*, 7 = *strongly agree*; McDonald's $\omega = .93$). A confirmatory factor analysis model in which all items loaded onto a single factor showed acceptable fit, $\chi^2 (20) = 111.90; \text{CFI} = 0.97; \text{TLI} = 0.95; \text{RMSEA} = 0.09, [0.08, 0.11]$.

We measured moral concerns with the 36-item moral foundations questionnaire [MFQ-2, @atari_morality_2022] which assesses to what extent participants endorse concerns about care, equality, proportionality, loyalty, authority, and purity (e.g., "I believe chastity is an important virtue."; 1 = *does not describe me at all*, 5 = *describes me extremely well*). We embedded three further attention checks within the questionnaire (e.g., "To show that you are paying attention and giving your best effort, please select 'moderately describes me'.").
